Data Flow Analysis\\in the Presence of Correlated Calls

### 2014-12-09 content/intro.tex

We present a formalization of the transformation and prove its correctness
as follows. First, we derive an ``Equivalence IDE problem'' from the original 
IFDS problem by associating the identity environment functions with all edges,
and show that the solution to this Equivalence IDE problem can be mapped back
to the solution of the original IFDS problem. Then, we derive a ``Correlated Calls 
IDE Problem' from the original IFDS problem and show how a solution to this problem 
can be mapped to the solution to the original IFDS problem, but also how an
more precise IFDS result can be derived from it. 
We also show that the correlated-calls analysis is sound, i.e., that it never considers concrete execution paths as infeasible.
This is illustrated schematically
in Figure~\ref{fig:transformations}%
\footnote{ 
  The labels $\result$, $\backEq$, $\backCC$, $\transEq$, and $\transCC$ on edges in 
  Figure~\ref{fig:transformations} reflect a number of mappings and projections 
  that will be defined in Section~\TODO{ref} and that can be ignored here.
}.  
\ftodo{would it make sense to add an edge in Figure~\ref{fig:transformations} from the IFDS problem to the IFDS result?}

>>>>

We present a formalization of the transformation and prove its correctness
as follows. First, we derive an ``Equivalence IDE problem'' from the original 
IFDS problem by associating the identity environment functions with all edges,
and show that the solution to this Equivalence IDE problem can be mapped back
to the solution of the original IFDS problem. Then, we derive a ``Correlated Calls 
IDE Problem'' from the original IFDS problem and show how a solution to this problem 
can be mapped to the solution to the original IFDS problem, but also how a
more precise IFDS result can be derived from it. 
\otodo{Do we need to mention the imprecise map from the CC-IDE result to the IFDS result? It
doesn't really seem relevant, and could be confusing.}
We also show that the correlated-calls analysis is sound, i.e., that it never considers concrete execution paths as infeasible.
This is illustrated schematically
in Figure~\ref{fig:transformations}%
\footnote{ 
  The labels $\result$, $\backEq$, $\backCC$, $\transEq$, and $\transCC$ on edges in 
  Figure~\ref{fig:transformations} reflect a number of mappings and projections 
  that will be defined in Section~\TODO{ref} and that can be ignored here.
}.  
\ftodo{would it make sense to add an edge in Figure~\ref{fig:transformations} from the IFDS problem to the IFDS result?}
